\begin{abstract}
The execution of long-horizon tasks under uncertainty is a fundamental
challenge in robotics. Recent approaches have made headway on these
tasks with an integration of task and motion
planning.  In this paper, we present Interfaced
Belief Space Planning (\ibsp), a modular approach to task and motion
planning in belief space. We use a task-independent interface layer to
combine an off-the-shelf classical planner and motion planner, enabling us to
solve complex problems in belief space. We determinize
the problem under the maximum likelihood observation assumption to obtain a
deterministic representation that can generate reasonable information-seeking
behavior. We leverage properties of maximum
likelihood determinizations to utilize a simple representation of
(optimistic) belief space dynamics that is well-suited to
planning. Our interface can be implemented with standard belief state
queries, requiring only the ability to sample, compute unnormalized
likelihoods, and answer maximum likelihood queries. Our contribution
is a novel algorithm for task and motion planning in belief space. The
algorithm is a novel approach that substantially reduces dependence on details of the belief
state dynamics. \ibsp{} can work with a broad class of black box state
estimators, with zero changes to the algorithm. We show that \ibsp{} is
complete for a (restricted) class of partially observable problems. We
validate our approach in simulated tasks for the PR2 that account for
continuous state, different belief distributions, and negative observations.
\end{abstract}
